Data analysis for employee cluster assessment

### 2023-08-07 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Adding option to remove other statuses

```{r}
make_elbow_d <- function(in_specification,
                         in_scale_or_rank,
                         in_working_or_observation_window,
                         in_weekday_correlation, 
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      method = "wss",
      nstart = 25,
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_silhouette_d <- function(in_specification,
                              in_scale_or_rank,
                              in_working_or_observation_window,
                              in_weekday_correlation, 
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      method = "silhouette",
      nstart = 25,
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_gap_stat_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation, 
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      nstart = 25,
      method = "gap_stat",
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_fviz_silhouette_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation,
                            in_clusters)
{
  step_01 <- 
    d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric))

@@

```{r}
elbows <- 
  specs %>%
   select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification
  ) %>%
   mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>% 
  pmap(make_elbow_d)
```

@@

```{r}
silhouette_scores <-
  specs %>%
  select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification
  ) %>%
  mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>%
  slice_head(n = 4) %>%
  pmap(make_silhouette_d)
```

@@

```{r}
gc()
gap_stats <- 
  specs %>%
   select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification
  ) %>%
   mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>% 
  pmap(make_gap_stat_d)
```

@@

```{r}
silhouette_diagrams <- 
  specs %>%
   select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification
  ) %>%
  distinct() %>% 
  slice(rep(1:n(), each = params$in_number_of_clusters_end)) %>% 
  rownames_to_column(var = "temp_01") %>% 
  mutate(temp_02 = as.numeric(temp_01),
         temp_03 = temp_02/params$in_number_of_clusters_end,
         temp_04 = ceiling(temp_03),
         temp_05 = temp_04*params$in_number_of_clusters_end-params$in_number_of_clusters_end,
         temp_06 = temp_02 - temp_05) %>% 
  rename(in_clusters = temp_06) %>% 
  select(-starts_with("temp_")) %>% 
  filter(in_clusters > 1) %>% 
  slice(2) %>%
  pmap(make_fviz_silhouette_d)
```

>>>>

```{r}
make_elbow_d <- function(in_specification,
                         in_scale_or_rank,
                         in_working_or_observation_window,
                         in_weekday_correlation, 
                         in_remove_other_statuses,
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation,
      in_remove_other_statuses = in_remove_other_statuses
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      method = "wss",
      nstart = 25,
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_silhouette_d <- function(in_specification,
                              in_scale_or_rank,
                              in_working_or_observation_window,
                              in_weekday_correlation,
                              in_remove_other_statuses,
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation,
      in_remove_other_statuses = in_remove_other_statuses
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      method = "silhouette",
      nstart = 25,
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_gap_stat_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation, 
                            in_remove_other_statuses,
                            in_max_clusters)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation,
      in_remove_other_statuses = in_remove_other_statuses
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(
      .,
      kmeans,
      k.max = in_max_clusters,
      nstart = 25,
      method = "gap_stat",
      nboot = 10,
      # algorithm="Lloyd",
      algorithm = "MacQueen",
      iter.max = 200,
      verbose = TRUE
    ) +
    theme_fivethirtyeight() +
  labs(
    subtitle = in_specification
  )
}

@@

```{r}
make_fviz_silhouette_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation,
                            in_remove_other_statuses,
                            in_clusters)
{
  step_01 <- 
    d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation,
      in_remove_other_statuses = in_remove_other_statuses
    ) %>%
    select(where(is.numeric))

@@

```{r}
elbows <- 
  specs %>%
   select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification,
    in_remove_other_statuses
  ) %>%
   mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>% 
  pmap(make_elbow_d)
```

@@

```{r}
silhouette_scores <-
  specs %>%
  select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification,
    in_remove_other_statuses
  ) %>%
  mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>%
  slice_head(n = 4) %>%
  pmap(make_silhouette_d)
```

@@

```{r}
gc()
gap_stats <- 
  specs %>%
   select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification,
    in_remove_other_statuses
  ) %>%
   mutate(
    in_max_clusters = params$in_number_of_clusters_end
    ) %>% 
  distinct() %>% 
  pmap(make_gap_stat_d)
```

@@

```{r}
silhouette_diagrams <- 
  specs %>%
    select(
    in_scale_or_rank,
    in_working_or_observation_window,
    in_weekday_correlation,
    in_specification,
    in_remove_other_statuses
  ) %>%
  distinct() %>% 
  slice(rep(1:n(), each = params$in_number_of_clusters_end)) %>% 
  rownames_to_column(var = "temp_01") %>% 
  mutate(temp_02 = as.numeric(temp_01),
         temp_03 = temp_02/params$in_number_of_clusters_end,
         temp_04 = ceiling(temp_03),
         temp_05 = temp_04*params$in_number_of_clusters_end-params$in_number_of_clusters_end,
         temp_06 = temp_02 - temp_05) %>% 
  rename(in_clusters = temp_06) %>% 
  select(-starts_with("temp_")) %>% 
  filter(in_clusters > 1) %>% 
  # slice(2) %>%
  pmap(make_fviz_silhouette_d)
```
